Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2021-12-22 Manuscript/FLPhish(Trans).tex
subsection:Designed Ensemble Federated Learning修改

\subsection{Designed Ensemble Federated Learning}
Inspired by ensemble learning, we propose a new FL architecture, called Ensemble FL.
\par Unlike existing FL architecture, which adopts gradient updates for global model updates, we apply an unlabeled dataset preserved by a central server and clients' predictions of it for global aggregation.
\subsubsection{{Client}} Each client {$c_{i}$} ($i$ indicates the number of the client) collects and labels its local data, which is from the personal computer, smartphone, smart cars and etc. The collected data is labeled and preprocessed by {$c_{i}$}, and {$c_{i}$} adopts the preprocessed local dataset to train its local model. When receiving a public dataset, {$c_{i}$} utilizes its local model to make predictions for the public dataset and return the predictions to the central server {$s$}.
\subsubsection{{Central server}} Central server {$s$} is responsible for making a public dataset and building a global model. The public dataset consists of a variety of unlabeled data. The dataset is collected by {$s$} or produced by it (such as using GAN to generate data). After the construction of the public dataset, {$s$} sends the public dataset to the clients. Each client {$c_{i}$} sends its predictions about the public dataset back to {$s$}. After receiving all the predictions, {$s$} aggregates the predictions. Then {$s$} employs the aggregated results and the public dataset to train the global model.

@@

  \item The selection of the global model and each client's local model is restricted to the same type of neural architecture in typical FL. Nevertheless, in our system, deploying different types of neural architectures is allowed by applying the distilled knowledge (the predictions of the unlabeled data produced by the clients). Different selected features in different clients are permitted as well.
  \item The overhead and latency of the communication process are significantly reduced compared to the typical FL architecture. Transferring data is much faster than transferring gradient updates. 
  \item The design of Ensemble FL can prevent the backdoor attack in FL. The detail of theoretical proof will be in the next section.
\end{itemize}

>>>>

\subsection{Designed Ensemble Federated Learning}
Inspired by ensemble learning, we propose a new FL architecture, called Ensemble FL.
\par Unlike existing FL architecture, which adopts clients' model gradient updates for global model updates, we apply an unlabeled dataset preserved by a central server and clients' predictions of it for global aggregation.
\subsubsection{{Client}} Each client {$c_{i}$} ($i$ indicates the serial number of the client) collects and labels its local data, which is from the personal computer, smartphone, smart cars and etc. The collected data is labeled and preprocessed by {$c_{i}$}, and {$c_{i}$} adopts the preprocessed local dataset to train its local model. When receiving a public dataset from the central server, {$c_{i}$} utilizes its local model to make predictions for the public dataset and return the predictions to the central server {$s$}.
\subsubsection{{Central server}} The central server {$s$} is responsible for making a public dataset and building a global model. The public dataset consists of a variety of unlabeled data whose labels are not possessed by the central server. The public dataset is collected by {$s$} or produced by it (such as using GAN to generate data). After the construction of the public dataset, {$s$} sends the public dataset to the clients. Each client {$c_{i}$} sends its predictions of the public dataset back to {$s$}. After receiving all the predictions, {$s$} aggregates the predictions to an aggregated predictions. Then {$s$} employs the aggregated predictions and the public dataset to train the global model.

@@

  \item The selection of the global model and each client's local model is restricted to the same type of neural architecture in typical FL. Nevertheless, in our system, deploying different types of neural architectures is allowed by applying the distilled knowledge (the predictions of the unlabeled data produced by the clients) instead of model gradient updates as the aggregation substances. Different selected features in different clients are permitted as well.
  \item The overhead and latency of the communication process are significantly reduced compared to the typical FL architecture. Transferring data is much faster than transferring gradient updates due to the smaller size. 
  \item The design of Ensemble FL can prevent the backdoor attack in FL. The detail of theoretical proof will be in the section B.
\end{itemize}
